Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2016-02-08 IEEE TSP/TeX/convergence_centralized.tex
updated TSP submission

The following conditions are required to show the convergence of Algorithm \ref{algo-1}, which is used to solve problems \eqref{eqn-6} and \eqref{eqn-mse-1} in an iterative manner.
\begin{itemize}
\item[(a)] Uniqueness of the minimizer in each step
\item[(b)] Objective function should be bounded below
\item[(c)] Feasible set should be compact
\item[(d)] Sequence of objective values should be strictly decreasing
\end{itemize}
The uniqueness condition in (a) is required to ensure strict monotonicity in the objective sequence. Therefore, upon satisfying the conditions (a)-(d), we can show that the objective sequence generated by Algorithm \ref{algo-1} converges, by using \cite[Th. 3.14]{rudin1964principles}. Then, by following the discussions in \cite{marks1978technical,lanckriet2009convergence,scutari_1}, we can show that \reviewF{every limit point of sequence of iterates is a stationary point of nonconvex problems in \eqref{eqn-6} and \eqref{eqn-mse-1}}.

@@

where \eqn{c > 0} be the constant of strong convexity, defined as \eqn{c \triangleq \min_{k} \{{\tau}_{k}^{(i)}\}}, and \eqn{\iter{\mbf{z}}{k+1}{i}} is the solution. Therefore, by using \eqref{strict_monotonicity} and \eqn{\iter{\mbf{z}}{k}{i} \in \iter{\mc{X}}{k}{i}}, we can show that \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})} holds strictly in each \ac{SCA} step unless \eqn{\mbf{z}_{k}^{(i)} \to \mbf{z}_{\lpoint}^{(i)}} as \eqn{k \to \infty}. Now, by utilizing the facts that (i) \eqn{\{f(\mbf{z}^{(i)}_k)\}} is monotonic, and (ii) the uniqueness of the minimizer (see \eqref{strict_monotonicity}), strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}} is ensured in each \ac{SCA} step \cite{scutari2010convex}. \reviewF{Furthermore, by using the fact that \eqn{\{f(\mbf{z}^{(i)}_k)\}} is also bounded, we can show that the objective sequence converges as \eqn{k \to \infty} in \ac{AO} step \eqn{i}, and let \eqn{\mbf{z}_{\lpoint}^{(i)} \triangleq [\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}]} be a stacked vector of the corresponding minimizer of \eqref{con-m} when \eqn{k \to \infty} in \ac{AO} step \eqn{i}.}

@@

Finally, to prove the global convergence of the \reviewF{objective sequence}, we need to show that the \ac{AO} updates also produce a nonincreasing sequence of objectives, \textit{i.e.}, 
\iftoggle{single_column}{
\begin{equation}
f(\iter{\mx}{\lpoint}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}).
\end{equation}}{
\begin{equation}
f(\iter{\mx}{\lpoint}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}).
\end{equation}}
Let \me{\iter{\mx}{\lpoint}{i}} and \me{\iter{\mz}{\lpoint|\my}{i}} be the solution obtained by solving \eqref{con-m} with respect to \eqn{\mx} and \eqn{\mz} by performing \ac{SCA} update as \eqn{k \to \infty} in the \me{\ith{i}} \ac{AO} step with fixed \eqn{\my = \iter{\my}{\lpoint}{i-1}}. In order to find \me{\iter{\my}{0}{i}}, we fix \eqn{\mx} as \me{\iter{\mx}{\lpoint}{i}} and solve problem \eqref{con-m} for \me{\my} and \eqn{\mz}. Since the constraint \eqref{con-dc-m} is linearized around \eqn{\iter{\mbf{z}}{\lpoint}{i}}, the fixed operating point is also included in the feasible set by following \eqref{con-sub-set} as \eqn{\{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}\} \in \iter{\mc{Y}}{0}{i}}, therefore, we have
\begin{equation} \label{fixed_point}
f(\iter{\mx}{\lpoint}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}).
\end{equation}
\reviewF{Now, by using \eqref{con-dc-m}, we can ensure that \eqn{\iter{\mbf{z}}{\lpoint}{i} \in \{ \iter{\mc{X}}{\lpoint}{i} \cap \iter{\mc{Y}}{0}{i} \}} in each \ac{AO} update \eqn{i} while alternating the optimization variables from \eqn{\mx,\mz} to \eqn{\my,\mz}. Moreover, due to strong convexity of the objective function \eqref{mod_obj}, by following \eqref{strict_monotonicity}, we can show that \eqref{fixed_point} holds with strict inequality in each \ac{AO} update unless the overall objective sequence converges. Now, by combining \eqref{con-convergence}, \eqref{strict_monotonicity} and \eqref{fixed_point}, we can ensure strictly nonincreasing nature of the objective sequence \eqn{\{f(\mbf{z}^{(i)}_k)\}} in each \ac{SCA} and \ac{AO} step.}

\subsection{Stationarity of Limit Points} \label{c-b}
\reviewF{We now discuss the convergence properties of sequence of iterates. For convenience, let us consider a unified superscript \eqn{t} to refer to the index of both \ac{SCA} and \ac{AO} procedures (\textit{i.e.}, index \eqn{t} denotes \ac{SCA} step \eqn{k} and \ac{AO} step \eqn{i}). Then, we denote iterate \eqn{\ma^t} as a vector formed by stacking the minimizer of \eqref{con-m} at iteration \eqn{t} as \eqn{\mat{t} = \mbf{z}^{(i)}_k}, and let \eqn{\{\mat{t}\}} be the sequence formed by collecting the minimizers of \eqref{con-m} from each iteration.

Note that the objective sequence \eqn{\{f(\ma^t)\}} is bounded and nonincreasing (see Appendices \ref{b_obj} and \ref{mcity}). Therefore, by using \cite[Prop. A.3]{bertsekas1999nonlinear}, we can ensure the convergence of \eqn{\{f(\ma^t)\}}. Unfortunately, such a claim cannot be made on the convergence of sequence of iterates \eqn{\{\ma^t\}}. However, due to compactness of the feasible set, the sequence of iterates \eqn{\{\ma^t\} \subset \mc{F}} is bounded. Therefore, the sequence \eqn{\{\mat{t}\}} has at least one limit such that there exists a subsequence of \eqn{\{\ma^t\}} that converges to it, by following \cite[Prop. A.5]{bertsekas1999nonlinear}.

@@

Now, by using the strict monotonicity of \eqn{\{f(\ma^{t_j})\}}, it follows that as \eqn{j \to \infty}, \eqn{\ma^{t_j} \to \bar{\ma}} and \eqn{f(\ma^{t_{j}}) - f(\ma^{t_{j+1}}) \to 0}. Moreover, since \eqn{\bar{\ma}} is the solution of \eqref{con-m}, it satisfies \eqref{strict_monotonicity} over convex subset \eqn{\mc{Q}}, which can either be \eqn{\iter{\mc{X}}{k}{i}} or \eqn{\iter{\mc{Y}}{k}{i}} as \eqn{k \to \infty, i \to \infty}. Using the above statements, we can show that \eqn{\bar{\ma}} satisfies the optimality condition  \cite[Prop. 2.1.2]{bertsekas1999nonlinear} as 
\begin{equation} \label{seq_mon1}
\nabla f (\bar{\ma})^\tran (\ma - \bar{\ma}) \geq 0, \; \fall \ma \in \mc{Q} \subset \mc{F} \eqsub.
\end{equation}
Thus, \eqn{\bar{\ma}} is a stationary point, and by using \eqref{limpoint}, we can show that every limit point of \eqn{\{\ma^t\}} is a stationary point of \eqref{con-m}.

@@

The relation between \eqref{kkt_expr} and \eqref{kkt_mod_expr} is evident by the following facts: (i) The quadratic term in \eqref{mod_obj} \eqn{\|\ma^{t_{j+1}} - \ma^{t_j}\|^2 \to 0}  as \eqn{j \to \infty, \ma^{t_j} \to \bar{\ma}}, since we assume that \eqn{\bar{\ma}} is the limit point of a convergent subsequence \eqn{\{\ma^{t_j}\}}. Therefore, the gradient evaluated at \eqn{\bar{\ma}} satisfies \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})}. (ii) Additionally, by using the continuity of function \eqn{g_o} and \eqref{con-relax}, equivalence between the gradient of \eqref{con-dc} and \eqref{con-dc-m} is obtained as \eqn{\ma^{t_j} \to \bar{\ma}}
\begin{equation} \label{rhs_equiv}
\nabla h(\bar{\ma}) - \nabla \hat{g}_o(\bar{\ma};\bar{\ma}) = \nabla h(\bar{\ma}) - \nabla g_o(\bar{\ma}).
\end{equation}
Now, by applying the relation \eqref{rhs_equiv} and \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})} in \eqref{kkt_mod_expr}, we can show that limit point \eqn{\bar{\ma}} satisfies \eqref{kkt_expr}. Finally, by following \cite[Thm. 2]{scutari_1} and \cite[Prop. 3.2]{amir}, we can show that every limit point of sequence of iterates \eqn{\{\ma^t\}} generated by the iterative method is a stationary point of problem \eqref{con}.}
%using \cite[Thms. 2 and 11]{scutari_1} and \cite[Prop. 3.2]{amir}, we can show that every limit point of sequence of iterates \eqn{\{\ma^t\}} generated by the iterative algorithm is a stationary point of problem \eqref{con}.}

>>>>

The following conditions are required to show the convergence of Algorithm \ref{algo-1}, which is used to solve problems \eqref{eqn-6} and \eqref{eqn-mse-1} in an iterative manner.
\begin{itemize}
\item[(a)] Uniqueness of the minimizer in each step
\item[(b)] Objective function should be bounded below
\item[(c)] Feasible set should be compact
\item[(d)] Sequence of objective values should be strictly decreasing
\end{itemize}
The uniqueness condition in (a) is required to ensure strict monotonicity in the objective sequence. Therefore, upon satisfying the conditions (a)-(d), we can show that the objective sequence generated by Algorithm \ref{algo-1} converges by using \cite[Th. 3.14]{rudin1964principles}. Then, by following the discussions in \cite{marks1978technical,lanckriet2009convergence,scutari_1}, we can show that every limit point of sequence of iterates is a stationary point of nonconvex problems in \eqref{eqn-6} and \eqref{eqn-mse-1}.

@@

where \eqn{c > 0} be the constant of strong convexity, defined as \eqn{c \triangleq \min_{k} \{{\tau}_{k}^{(i)}\}}, and \eqn{\iter{\mbf{z}}{k+1}{i}} is the solution. Therefore, by using \eqref{strict_monotonicity} and \eqn{\iter{\mbf{z}}{k}{i} \in \iter{\mc{X}}{k}{i}}, we can show that \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})} holds strictly in each \ac{SCA} step unless \eqn{\mbf{z}_{k}^{(i)} \to \mbf{z}_{\lpoint}^{(i)}} as \eqn{k \to \infty}. Now, by utilizing the facts that (i) \eqn{\{f(\mbf{z}^{(i)}_k)\}} is monotonic, and (ii) the uniqueness of the minimizer (see \eqref{strict_monotonicity}), strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}} is ensured in each \ac{SCA} step \cite{scutari2010convex}. Furthermore, by using the fact that \eqn{\{f(\mbf{z}^{(i)}_k)\}} is also bounded, we can show that the objective sequence converges as \eqn{k \to \infty} in \ac{AO} step \eqn{i}, and let \eqn{\mbf{z}_{\lpoint}^{(i)} \triangleq [\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}]} be a stacked vector of the corresponding minimizer of \eqref{con-m} when \eqn{k \to \infty} in \ac{AO} step \eqn{i}.

@@

Finally, to prove the global convergence of the objective sequence, we need to show that the \ac{AO} updates also produce a nonincreasing sequence of objectives, \textit{i.e.}, 
\iftoggle{single_column}{
\begin{equation}
f(\iter{\mx}{\lpoint}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}).
\end{equation}}{
\begin{equation}
f(\iter{\mx}{\lpoint}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}).
\end{equation}}
Let \me{\iter{\mx}{\lpoint}{i}} and \me{\iter{\mz}{\lpoint|\my}{i}} be the solution obtained by solving \eqref{con-m} with respect to \eqn{\mx} and \eqn{\mz} by performing \ac{SCA} update as \eqn{k \to \infty} in the \me{\ith{i}} \ac{AO} step with fixed \eqn{\my = \iter{\my}{\lpoint}{i-1}}. In order to find \me{\iter{\my}{0}{i}}, we fix \eqn{\mx} as \me{\iter{\mx}{\lpoint}{i}} and solve problem \eqref{con-m} for \me{\my} and \eqn{\mz}. Since the constraint \eqref{con-dc-m} is linearized around \eqn{\iter{\mbf{z}}{\lpoint}{i}}, the fixed operating point is also included in the feasible set by following \eqref{con-sub-set} as \eqn{\{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}\} \in \iter{\mc{Y}}{0}{i}}, therefore, we have
\begin{equation} \label{fixed_point}
f(\iter{\mx}{\lpoint}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}).
\end{equation}
Now, by using \eqref{con-dc-m}, we can ensure that \eqn{\iter{\mbf{z}}{\lpoint}{i} \in \{ \iter{\mc{X}}{\lpoint}{i} \cap \iter{\mc{Y}}{0}{i} \}} in each \ac{AO} update \eqn{i} while alternating the optimization variables from \eqn{\mx,\mz} to \eqn{\my,\mz}. Moreover, due to strong convexity of the objective function \eqref{mod_obj}, by following \eqref{strict_monotonicity}, we can show that \eqref{fixed_point} holds with strict inequality in each \ac{AO} update unless the overall objective sequence converges. Now, by combining \eqref{con-convergence}, \eqref{strict_monotonicity} and \eqref{fixed_point}, we can ensure strictly nonincreasing nature of the objective sequence \eqn{\{f(\mbf{z}^{(i)}_k)\}} in each \ac{SCA} and \ac{AO} step.

\subsection{Stationarity of Limit Points} \label{c-b}
We now discuss the convergence properties of sequence of iterates. For convenience, let us consider a unified superscript \eqn{t} to refer to the index of both \ac{SCA} and \ac{AO} procedures (\textit{i.e.}, index \eqn{t} denotes \ac{SCA} step \eqn{k} and \ac{AO} step \eqn{i}). Then, we denote iterate \eqn{\ma^t} as a vector formed by stacking the minimizer of \eqref{con-m} at iteration \eqn{t} as \eqn{\mat{t} = \mbf{z}^{(i)}_k}, and let \eqn{\{\mat{t}\}} be the sequence formed by collecting the minimizers of \eqref{con-m} from each iteration.

Note that the objective sequence \eqn{\{f(\ma^t)\}} is bounded and nonincreasing (see Appendices \ref{b_obj} and \ref{mcity}). Therefore, by using \cite[Prop. A.3]{bertsekas1999nonlinear}, we can ensure the convergence of \eqn{\{f(\ma^t)\}}. Unfortunately, such a claim cannot be made on the convergence of sequence of iterates \eqn{\{\ma^t\}}. However, due to compactness of the feasible set, the sequence of iterates \eqn{\{\ma^t\} \subset \mc{F}} is bounded. Therefore, the sequence \eqn{\{\mat{t}\}} has at least one limit such that there exists a subsequence of \eqn{\{\ma^t\}} that converges to it by following \cite[Prop. A.5]{bertsekas1999nonlinear}.

@@

Now, by using the strict monotonicity of \eqn{\{f(\ma^{t_j})\}}, it follows that as \eqn{j \to \infty}, \eqn{\ma^{t_j} \to \bar{\ma}} and \eqn{f(\ma^{t_{j}}) - f(\ma^{t_{j+1}}) \to 0}. Furthermore, since \eqn{\bar{\ma}} is the solution of \eqref{con-m}, it satisfies \eqref{strict_monotonicity} over convex subset \eqn{\mc{Q}}, which can either be \eqn{\iter{\mc{X}}{k}{i}} or \eqn{\iter{\mc{Y}}{k}{i}} as \eqn{k \to \infty, i \to \infty}. Using the above statements, we can show that \eqn{\bar{\ma}} satisfies the optimality condition  \cite[Prop. 2.1.2]{bertsekas1999nonlinear} as 
\begin{equation} \label{seq_mon1}
\nabla f (\bar{\ma})^\tran (\ma - \bar{\ma}) \geq 0, \; \fall \ma \in \mc{Q} \subset \mc{F} \eqsub
\end{equation}
thus, \eqn{\bar{\ma}} is a stationary point. Moreover, by using \eqref{limpoint}, we can show that every limit point of \eqn{\{\ma^t\}} is a stationary point of~\eqref{con-m}.

@@

The relation between \eqref{kkt_expr} and \eqref{kkt_mod_expr} is evident by the following facts: (i) The quadratic term in \eqref{mod_obj} \eqn{\|\ma^{t_{j+1}} - \ma^{t_j}\|^2 \to 0}  as \eqn{j \to \infty, \ma^{t_j} \to \bar{\ma}}, since we assume that \eqn{\bar{\ma}} is the limit point of a convergent subsequence \eqn{\{\ma^{t_j}\}}. Therefore, the gradient evaluated at \eqn{\bar{\ma}} satisfies \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})}. (ii) Additionally, by using the continuity of function \eqn{g_o} and \eqref{con-relax}, equivalence between the gradient of \eqref{con-dc} and \eqref{con-dc-m} is obtained as \eqn{\ma^{t_j} \to \bar{\ma}}
\begin{equation} \label{rhs_equiv}
\nabla h(\bar{\ma}) - \nabla \hat{g}_o(\bar{\ma};\bar{\ma}) = \nabla h(\bar{\ma}) - \nabla g_o(\bar{\ma}).
\end{equation}
Now, by applying the relation \eqref{rhs_equiv} and \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})} in \eqref{kkt_mod_expr}, we can show that limit point \eqn{\bar{\ma}} satisfies \eqref{kkt_expr}. Finally, by following \cite[Thm. 2]{scutari_1} and \cite[Prop. 3.2]{amir}, we can show that every limit point of sequence of iterates \eqn{\{\ma^t\}} generated by the iterative method is a stationary point of problem \eqref{con}.
%using \cite[Thms. 2 and 11]{scutari_1} and \cite[Prop. 3.2]{amir}, we can show that every limit point of sequence of iterates \eqn{\{\ma^t\}} generated by the iterative algorithm is a stationary point of problem \eqref{con}.}

### 2016-02-08 IEEE TSP/TeX/introduction.tex
updated TSP submission

%The last mile wireless connectivity poses significant bottleneck in the overall data traffic for the interconnected networks. The main challenges in the wireless networks are due to the scarcity of the available resources either in terms of power or spectrum usage and the complexity of the receiver algorithms which impacts the mobile battery consumption. In order to overcome the receiver complexity, \ac{OFDM} is introduced for the wide band transmissions. To improve data rate, multiple antennas are installed at \acp{BS} and/or at user terminals to avail additional freedom in the form of spatial dimension. The inclusion of \ac{MIMO} technique in wireless networks provides higher data rate or lower outage for the same transmission power and bandwidth.
In a network with multiple \acp{BS} serving multiple users, the main driving factor for the transmission is the packets waiting at each \ac{BS} corresponding to the different users existing in the network. We consider the problem of transmit precoder design and resource allocation over the space-frequency resources provided by the \ac{MIMO} \ac{OFDM} framework in the downlink \ac{IBC} to minimize the number of queued packets in the \acp{BS}. Thus, the problem of interest inherently includes resource allocation of users associated with different \acp{BS}.

>>>>

%The last mile wireless connectivity poses significant bottleneck in the overall data traffic for the interconnected networks. The main challenges in the wireless networks are due to the scarcity of the available resources either in terms of power or spectrum usage and the complexity of the receiver algorithms which impacts the mobile battery consumption. In order to overcome the receiver complexity, \ac{OFDM} is introduced for the wide band transmissions. To improve data rate, multiple antennas are installed at \acp{BS} and/or at user terminals to avail additional freedom in the form of spatial dimension. The inclusion of \ac{MIMO} technique in wireless networks provides higher data rate or lower outage for the same transmission power and bandwidth.
In a network with multiple \acp{BS} serving multiple users, the driving factor for the transmission is the packets waiting at each \ac{BS} corresponding to the users in the network. We consider the problem of transmit precoder design and resource allocation over the space-frequency resources provided by the \ac{MIMO} \ac{OFDM} framework in the downlink \ac{IBC} to reduce the number of queued packets in the \acp{BS}. %Thus, the problem of interest inherently includes resource allocation of users associated with different \acp{BS}.

### 2016-02-08 IEEE TSP/TeX/mse_formulation.tex
updated TSP submission

In all our numerical simulations, the objective sequence generated by Algorithm \ref{algo-1} converges. \reviewF{However, to provide a formal convergence analysis, we consider using a regularized objective in \eqref{mod_obj} instead of using \eqref{eqn-6.1} and \eqref{eqn-mse-1.1}. The proximal term in \eqref{mod_obj} ensures strong convexity, thereby enforcing the uniqueness of the minimizer in each iteration. Note that the feasible set of problems \eqref{eqn-3} and \eqref{eqn-mse-1} is bounded. However, for problem \eqref{eqn-6}, the feasible set need not be bounded due to newly introduced variables in \eqref{eqn-6.2} and \eqref{eqn-6.3} to relax the \ac{SINR} expression in \eqref{eq:SINR}. This follows from the fact that  \eqn{\beta_{l,k,n}} can take any value by satisfying \eqref{eqn-6.3} without violating the constraints of problem \eqref{eqn-6} when \eqn{\gamma_{l,k,n} = 0}. Nevertheless, we can limit \eqn{\beta_{l,k,n}}'s by using a maximum interference threshold depending on \eqn{P_{\max}} and the channel gains, and thus the feasible set can be bounded without affecting the optimality of the considered problem. With the above assumptions, convergence analysis of Algorithm \ref{algo-1} is discussed in Appendix \ref{sec-3.5}.}

>>>>

In all our numerical simulations, the objective sequence generated by Algorithm \ref{algo-1} converges. However, to provide a formal convergence analysis, we consider using a regularized objective in \eqref{mod_obj} instead of using \eqref{eqn-6.1} and \eqref{eqn-mse-1.1}. The proximal term in \eqref{mod_obj} ensures strong convexity, thereby enforcing the uniqueness of the minimizer in each iteration. Note that the feasible set of problems \eqref{eqn-3} and \eqref{eqn-mse-1} is bounded. However, for problem \eqref{eqn-6}, the feasible set need not be bounded due to newly introduced variables in \eqref{eqn-6.2} and \eqref{eqn-6.3} to relax the \ac{SINR} expression in \eqref{eq:SINR}. This follows from the fact that  \eqn{\beta_{l,k,n}} can take any value by satisfying \eqref{eqn-6.3} without violating the constraints of problem \eqref{eqn-6} when \eqn{\gamma_{l,k,n} = 0}. Nevertheless, we can limit \eqn{\beta_{l,k,n}}'s by using a maximum interference threshold depending on \eqn{P_{\max}} and the channel gains, and thus the feasible set can be bounded without affecting the optimality of the considered problem. With the above assumptions, convergence analysis of Algorithm \ref{algo-1} is discussed in Appendix \ref{sec-3.5}.

### 2016-02-08 IEEE TSP/TeX/system_model.tex
updated TSP submission

We adopt linear transmit beamforming technique at \acp{BS}. Specifically, the data symbols \me{d_{l,k,n}} for  user \me{k} on the \me{\ith{l}} spatial stream over sub-channel \me{n} is multiplied with beamformer \me{\mvec{m}{l,k,n} \in \mathbb{C}^{N_T \times 1}} before being transmitted. In order to detect  multiple spatial streams at the user terminal, receive beamforming vector \me{\mvec{w}{l,k,n}} is employed for each user. Consequently, the received data estimate corresponding to the \me{\ith{l}} spatial stream over sub-channel \me{n} at user $k$ is given by
\iftoggle{single_column}{
\begin{equation}\label{eqn-1}
\hat{d}_{l,k,n} = \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \sum_{j = 1}^L \mvec{m}{j,k,n} d_{j,k,n} + \mvec{w}{l,k,n}^\herm \sum_{i \in \mc{U} \backslash \set{k}} \mvec{H}{b_i,k,n} \sum_{j = 1}^L \mvec{m}{j,i,n}d_{j,i,n} + \mvec{w}{l,k,n}^\herm \mvec{n}{l,k,n}
\end{equation}
}{
\begin{multline}\label{eqn-1}
\hat{d}_{l,k,n} = \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \sum_{j = 1}^L \mvec{m}{j,k,n} d_{j,k,n} + \mvec{w}{l,k,n}^\herm \mvec{n}{l,k,n} \\ 
+ \mvec{w}{l,k,n}^\herm \sum_{i \in \mc{U} \backslash \set{k}} \mvec{H}{b_i,k,n} \sum_{j = 1}^L \mvec{m}{j,i,n}d_{j,i,n}
\end{multline}
}
where \me{\mvec{H}{b,k,n} \in \mathbb{C}^{N_R \times N_T}} is the channel between \ac{BS} \me{b} and  user \me{k} on sub-channel \me{n}, and \me{\mvec{n}{l,k,n}} \me{\sim \mc{CN}(0,N_0)} is the additive noise vector for user \me{k} on the \me{\ith{n}} sub-channel and \me{\ith{l}} spatial stream. In \eqref{eqn-1}, \me{L = \text{rank}(\mvec{H}{b,k,n}) = \min(N_T,N_R)} is the maximum number of spatial streams.\footnote{It can be easily extended for user specific streams \me{L_k} instead of using common \me{L} streams for all users. \me{L} streams are initialized but after solving the problem, only \me{L_{k,n} \leq L} non-zero data streams are transmitted.} Assuming independent detection of data streams, we can write the signal-to-interference-plus-noise ratio (SINR) as
\begin{equation}\label{eq:SINR}
\gamma_{l,k,n} = \dfrac{\left |\mvec{w}{l,k,n}^\herm \, \mvec{H}{b_k,k,n} \, \mvec{m}{l,k,n} \right |^2}{\enoise + \sum_{(j,i) \neq (l,k)} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2}
\end{equation}
where \me{\enoise = N_0 \, \trace (\mvec{w}{l,k,n} \mbf{w}_{l,k,n}^\herm)} denotes the equivalent noise variance. In order to avoid the overhead involved in feeding back the user channels, we consider \ac{TDD} system in which \acp{BS} can estimate the downlink channels from uplink pilots by using channel reciprocity property.

Let \me{Q_k} be the number of backlogged packets destined for user \me{k} at a given scheduling instant. The queue dynamics of user \me{k} are modeled using the Poisson arrival process with the average number of packet arrivals of \me{A_k = \mathbf{E}_i\{\lambda_k\}} packets or bits, where \me{\lambda_k(i) \sim \mathrm{Pois}(A_k)} represents the instantaneous number of packets arriving for user \me{k} at the \me{\ith{i}} time instant.\footnote{The unit can either be packets or bits as long as the arrival and the transmission units are similar.} The total number of queued packets at the \me{\ith{(i+1)}} instant for user \me{k}, denoted as \me{Q_k(i+1)}, is given by
\begin{equation}
Q_k(i+1) = \Big [ Q_k(i) - t_k(i) \Big ]^+ + \lambda_k(i)
\label{eqn-2a}
\end{equation}
where \me{[x]^+ \equiv \max{ \lbrace x,0  \rbrace}} and \me{t_k} denotes the number of transmitted packets or bits for user \me{k}. At the \me{\ith{i}} instant, the transmission rate of user \me{k} is given by
\begin{equation}
t_k(i) = \sum_{n = 1}^N \, \sum_{l = 1}^L \, t_{l,k,n}(i)
\end{equation}
where \me{t_{l,k,n}} denotes the number of transmitted packets or bits over the \me{\ith{l}} spatial stream on the \me{\ith{n}} sub-channel. The maximum rate achieved over the space-frequency resource \me{(l,n)} is given by \me{t_{l,k,n} \leq \log_2(1 + \gamma_{l,k,n})} for the \ac{SINR} \me{\gamma_{l,k,n}}.\footnote{The upper bound can be achieved by using Gaussian signaling.} Note that \me{t_k} and \me{Q_k} are represented by the same units, \textit{i.e.}, in bits defined per channel use.

>>>>

We adopt linear transmit beamforming technique at \acp{BS}. Specifically, the data symbols \me{d_{l,k,n}} for  user \me{k} on the \me{\ith{l}} spatial stream over sub-channel \me{n} is multiplied with beamformer \me{\mvec{m}{l,k,n} \in \mathbb{C}^{N_T \times 1}} before being transmitted. In order to detect  multiple spatial streams at the user terminal, receive beamforming vector \me{\mvec{w}{l,k,n}} is employed for each user. Consequently, the received data estimate corresponding to the \me{\ith{l}} spatial stream over sub-channel \me{n} at user $k$ is given by
\iftoggle{single_column}{
\begin{equation}\label{eqn-1}
\hat{d}_{l,k,n} = \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \sum_{j = 1}^L \mvec{m}{j,k,n} d_{j,k,n} + \mvec{w}{l,k,n}^\herm \sum_{i \in \mc{U} \backslash \set{k}} \mvec{H}{b_i,k,n} \sum_{j = 1}^L \mvec{m}{j,i,n}d_{j,i,n} + \mvec{w}{l,k,n}^\herm \mvec{n}{l,k,n}
\end{equation}
}{
\begin{multline}\label{eqn-1}
\hat{d}_{l,k,n} = \textstyle \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \sum_{j = 1}^L \mvec{m}{j,k,n} d_{j,k,n} + \mvec{w}{l,k,n}^\herm \mvec{n}{l,k,n} \\ 
+ \mvec{w}{l,k,n}^\herm \sum_{i \in \mc{U} \backslash \set{k}} \mvec{H}{b_i,k,n} \sum_{j = 1}^L \mvec{m}{j,i,n}d_{j,i,n}
\end{multline}
}
where \me{\mvec{H}{b,k,n} \in \mathbb{C}^{N_R \times N_T}} is the channel between \ac{BS} \me{b} and  user \me{k} on sub-channel \me{n}, and \me{\mvec{n}{l,k,n}} \me{\sim \mc{CN}(0,N_0)} is the additive noise vector for user \me{k} on the \me{\ith{n}} sub-channel and \me{\ith{l}} spatial stream. In \eqref{eqn-1}, \me{L = \text{rank}(\mvec{H}{b,k,n}) = \min(N_T,N_R)} is the maximum number of spatial streams.\footnote{It can be easily extended for user specific streams \me{L_k} instead of using common \me{L} streams for all users. \me{L} streams are initialized but after solving the problem, only \me{L_{k,n} \leq L} non-zero data streams are transmitted.} Assuming independent detection of data streams, we can write the signal-to-interference-plus-noise ratio (SINR) as
\begin{equation}\label{eq:SINR}
\gamma_{l,k,n} = \dfrac{\left |\mvec{w}{l,k,n}^\herm \, \mvec{H}{b_k,k,n} \, \mvec{m}{l,k,n} \right |^2}{\enoise + \sum_{(j,i) \neq (l,k)} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2}
\end{equation}
where \me{\enoise = N_0 \, \trace (\mvec{w}{l,k,n} \mbf{w}_{l,k,n}^\herm)} denotes the equivalent noise variance. In order to avoid the overhead involved in feeding back the user channels, we consider \ac{TDD} system in which \acp{BS} can estimate the downlink channels from uplink pilots by using channel reciprocity property.

Let \me{Q_k} be the number of backlogged packets destined for user \me{k} at a given scheduling instant. The queue dynamics of user \me{k} are modeled using the Poisson arrival process with the average number of packet arrivals of \me{A_k = \mathbf{E}_i\{\lambda_k\}} packets or bits, where \me{\lambda_k(i) \sim \mathrm{Pois}(A_k)} represents the instantaneous number of packets arriving for user \me{k} at the \me{\ith{i}} time instant.\footnote{The unit can either be packets or bits as long as the arrival and the transmission units are similar.} The total number of queued packets at the \me{\ith{(i+1)}} instant for user \me{k}, denoted as \me{Q_k(i+1)}, is given by
\begin{equation}
Q_k(i+1) = \Big [ Q_k(i) - t_k(i) \Big ]^+ + \lambda_k(i)
\label{eqn-2a}
\end{equation}
where \me{[x]^+ \equiv \max{ \lbrace x,0  \rbrace}} and \me{t_k} denotes the number of transmitted packets or bits for user \me{k}. At the \me{\ith{i}} instant, the transmission rate of user \me{k} is given by
\begin{equation}
t_k(i) = \sum_{n = 1}^N \, \sum_{l = 1}^L \, t_{l,k,n}(i)
\end{equation}
where \me{t_{l,k,n}} denotes the number of transmitted packets or bits over the \me{\ith{l}} spatial stream on the \me{\ith{n}} sub-channel. The maximum rate achieved over the space-frequency resource \me{(l,n)} is given by \me{t_{l,k,n} \leq \log_2(1 + \gamma_{l,k,n})} for the \ac{SINR} \me{\gamma_{l,k,n}}.\footnote{The upper bound can be achieved by using Gaussian signaling.} The variables \me{t_k} and \me{Q_k} are represented by the same units, \textit{i.e.}, in bits defined per channel use.
